### 2020-02-20 README.Rmd
Increase test coverage, and fixing the UI
adding travis

<!-- badges: start -->
<!-- badges: end -->

@@

```{r echo = FALSE}
library(oolong)
library(stm)
library(quanteda)
library(dplyr)
```

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
<!-- badges: end -->

@@

```{r}
library(oolong)
library(stm)
library(quanteda)
library(dplyr)
```
